### 2025-02-14 paper/sections/other/constraints.qmd
more work on plot

using CTExperiments
using CTExperiments.CounterfactualExplanations
using CTExperiments.CounterfactualTraining
using CTExperiments.Flux
using CTExperiments.Plots
using CTExperiments.TaijaPlotting
```

@@

    # Data and decision boundary:
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data, label=["1=Default" "2=No Default"], xlab=xlab, ylab=ylab, title="Iteration $(_itercount)")
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")

@@

    if _itercount == 1
        push!(_plts, plt)
    end
    global _itercount += 1
end

# Data:
specs = [
    (VanillaObjective(needs_ce=true), ["both", "both"]),
    (EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    (EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```

@@

for (obj, constraint) in specs

@@

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 10,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

    push!(models, model)
    push!(_plts, current())
    push!(plts, _plts)
end
```

@@

using Plots.PlotMeasures
plts = []
titles = ["(a)", "(b)"]
_xlab = "Existing Debt"
_ylab = "Age"
for (i,model) in enumerate(models)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    xlab = constraints[i][1] == "both" ? "$(_xlab) (mutable)" : "$(_xlab) (immutable)"
    ylab = constraints[i][2] == "both" ? "$(_ylab) (mutable)" : "$(_ylab) (immutable)"
    plt = Plots.scatter(ce_data; xlab=xlab, ylab=ylab, bottom_margin = 5mm, left_margin = 5mm, label=["Default" "No Default"], title=titles[i])
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")

>>>>

using CTExperiments
using CTExperiments.CounterfactualExplanations
using CTExperiments.CounterfactualTraining
using CTExperiments.Flux
using CTExperiments.Plots
using CTExperiments.TaijaPlotting
using Plots.PlotMeasures
```

@@

    # Data and decision boundary:
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(
        ce_data, 
        title="Iteration $(_itercount)",
        # label=["1=Default" "2=No Default"], 
        # legend_position=:topright, 
        bottom_margin = 5mm, 
        left_margin = 5mm, 
        xlab=xlab, ylab=ylab,  
        axis=nothing, 
        legend=false
    )
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")

    # # Gradient field:
    # u = []
    # v = []
    # for (x, y) in inputs
    #     g = -loss_grads(generator, M, ce, [x, y][:,:])
    #     push!(u, η * g[1])
    #     push!(v, η * g[2])
    # end
    # Plots.quiver!(x1, x2, quiver=(u, v))

@@

    if _itercount == 5
        push!(_plts, plt)
    end
    global _itercount += 1
end

# Data:
specs = [
    ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    ("(b)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    ("(c)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```

@@

for (title, obj, constraint) in specs

@@

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 50,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

    push!(models, model)
    push!(_plts, current())
    plt = Plots.plot(_plts..., plot_title = title, layout=(2,1))
    push!(plts, plt)
end
```

@@

plts = []
titles = ["(a)", "(b)"]
_xlab = "Existing Debt"
_ylab = "Age"
for (i,model) in enumerate(models)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    xlab = constraints[i][1] == "both" ? "$(_xlab) (mutable)" : "$(_xlab) (immutable)"
    ylab = constraints[i][2] == "both" ? "$(_ylab) (mutable)" : "$(_ylab) (immutable)"
    plt = Plots.scatter(ce_data; xlab=xlab, ylab=ylab, bottom_margin = 5mm, left_margin = 5mm, label=["Default" "No Default"], title=titles[i])
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
